---
pdf_document: default
author: "Sie Choon Hong"
date: "`r Sys.Date()`"
output:
  html_document: null
  df_print: paged
  pdf_document: default
title: 'Week-4: Code-along'
---

  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# II. Code to edit and execute using the Code-along.Rmd file 
<br>
<div id="home">
# Table of Content (Click the link below to scroll down to the specific content)
</div>
<a href="#q1">1. Loading packages (Slide #16)</a><br>
<a href="#q2">2. Loading data-set (Slide #16)</a><br>
<a href="#q3">3. List names of the variables in the data-set (Slide #19)</a><br>
<a href="#q4">4. Glimpse of contents of the data-set (Slide #20)</a>
<a href="#q5">5. Select a single column (Slide #24)
</a><br>
<a href="#q6">6. Select multiple columns (Slide #25)
</a><br>
<a href="#q7">7. Arrange entries of a column (Slide #28)
</a><br>
<a href="#q8">8. Arrange entries of a column in the descending order (Slide #30)</a><br>
<a href="#q9">9. Select columns and arrange the entries of a column (Slide #31)</a><br>
<a href="#q10">10. Select columns and arrange the entries of a column using the pipe operator (Slide #37)</a><br>
<a href="#q11">11. Pick rows matching a condition (Slide #44)</a><br>
<a href="#q12">12. Pick rows matching multiple conditions (Slide #46)
</a><br>
<a href="#q13">13. Non-conditional selection of rows: sequence of indices (Slide #49)</a><br>
<a href="#q14">14. Non-conditional selection of rows: non-consecutive/specific indices (Slide #50)</a><br>
<a href="#q15">15. Pick unique rows using distinct() (Slide #52)
</a><br>
<a href="#q16">16. Creating a single column with mutate() (Slide #56)
</a><br>
<a href="#q17">17. Creating multiple columns with mutate() (Slide #58)
</a><br>
<a href="#q18">18. count() to get frequencies (Slide #60)
</a><br>
<a href="#q19">19. count() to get frequencies with sorting of count (Slide #61)</a><br>
<a href="#q20">20. count() multiple variables (Slide #62)</a><br>
<a href="#q21">21. summarise() for summary statistics (Slide #63)</a><br>
<a href="#q22">22. summarise() by using group_by to find mean (Slide #64)</a><br>
<a href="#q23">23. summarise() by using group_by to get count (Slide #65)</a><br>
<a href="#q24">24. summarise() for multiple summary statistics (Slide #67)</a><br>
<a href="#q25">25. select(), slice() and arrange() (Slide #68)</a><br>
<a href="#q26">26. select(), arrange() and slice() (Slide #69)</a><br>
<a href="#q27">27. filter() to select rows based on conditions (Slide #73)</a><br>
<a href="#q28">28. filter() to select rows based on complicated conditions (Slide #74)</a><br>
<a href="#q29">29. count() and arrange() (Slide #76)</a><br>
<a href="#q30">30. mutate(), select() and arrange() (Slide #77)</a><br>
<a href="#q31">31. mutate(), filter() and select() (Slide #78)</a><br>

<br>

## A. Data Wrangling
<br>
<div id="q1">
### 1. Loading packages (Slide #16) <a href=#home>Click Me to scroll to top</a>
```{r, eval=TRUE,echo=TRUE}
# Load package tidyverse
library("tidyverse")
```
</div>
<div id="q2">
### 2. Loading data-set (Slide #16) <a href=#home>Click Me to scroll to top</a>
```{r, eval=TRUE,echo=TRUE}
# Read data from the hotels.csv file and assign it to a variable named, "hotels"
hotels <- read_csv("hotels.csv")
```
</div>
<div id="q3">
### 3. List names of the variables in the data-set (Slide #19) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
names(hotels)
```
</div>
<div id="q4">
### 4. Glimpse of contents of the data-set (Slide #20) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
glimpse(hotels)
```
</div><br>

## B. Choosing rows or columns
<br>
<div id="q5">
### 5. Select a single column (Slide #24) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
select(hotels, lead_time)
```
</div><div id="q6">
### 6. Select multiple columns (Slide #25) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
select(hotels, lead_time,agent,market_segment)
```
</div><div id="q7">
### 7. Arrange entries of a column (Slide #28) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
arrange(hotels, lead_time)
```
</div><div id="q8">
### 8. Arrange entries of a column in the descending order (Slide #30) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
arrange(hotels, desc(lead_time))
```
</div><div id="q9">
### 9. Select columns and arrange the entries of a column (Slide #31) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
arrange(
  select(hotels, lead_time), desc(lead_time)
)
```
</div><div id="q10">
### 10. Select columns and arrange the entries of a column using the pipe operator (Slide #37) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
select(lead_time) %>%
arrange(desc(lead_time))
```
</div><div id="q11">
### 11. Pick rows matching a condition (Slide #44) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% 
  filter(children >= 1) %>% 
    select(hotel, children)
```
</div><div id="q12">
### 12. Pick rows matching multiple conditions (Slide #46) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% 
  filter(children >= 1,hotel == "City Hotel") %>%
    select(hotel, children)
```
</div><div id="q13">
### 13. Non-conditional selection of rows: sequence of indices (Slide #49) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% slice(1:5)
```
</div><div id="q14">
### 14. Non-conditional selection of rows: non-consecutive/specific indices (Slide #50) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% 
  slice(1,3,5)
```
</div><div id="q15">
### 15. Pick unique rows using distinct() (Slide #52) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% distinct(hotel)
```
</div><br>

## C. Creating new columns
<br>
<div id="q16">
### 16. Creating a single column with mutate() (Slide #56) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  mutate(little_ones = children + babies) %>%
  select(hotel, little_ones,children,babies)
```
</div><div id="q17">
### 17. Creating multiple columns with mutate() (Slide #58) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  mutate(little_ones = children + babies,
  average_little_ones = mean(little_ones)) %>%
  select(hotel, little_ones,children,babies, average_little_ones)
```
</div><br>

## D. More operations with examples
<br>
<div id="q18">
### 18. count() to get frequencies (Slide #60) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  count(market_segment)
```
</div><div id="q19">
### 19. count() to get frequencies with sorting of count (Slide #61) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  count(market_segment, sort = TRUE)
```
</div><div id="q20">
### 20. count() multiple variables (Slide #62) <a href=#home>scroll to top</a> <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  count(hotel, market_segment)
```

</div><div id="q21">
### 21. summarise() for summary statistics (Slide #63) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  summarise(mean_adr = mean(adr))
```
</div><div id="q22">
### 22. summarise() by using group_by to find mean (Slide #64)  <a href=#home>Click Me to scroll to top</a>
```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  group_by(hotel) %>%
  summarise(mean_adr = mean(adr))
```
</div><div id="q23">
### 23. summarise() by using group_by to get count (Slide #65) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  group_by(hotel) %>%
  summarise(count = n())
```
</div><div id="q24">
### 24. summarise() for multiple summary statistics (Slide #67) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  summarise(
  min_adr = min(adr),
  mean_adr = mean(adr),
  median_adr = median(adr),
  max_adr = max(adr)
)
```
</div><div id="q25">
### 25. select(), slice() and arrange() (Slide #68) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  select(hotel, lead_time) %>%
    slice(1:5) %>%
      arrange(lead_time)
```
</div><div id="q26">
### 26. select(), arrange() and slice() (Slide #69) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  select(hotel, lead_time) %>%
  arrange(lead_time) %>%
  slice(1:5)
```
</div><div id="q27">
### 27. filter() to select rows based on conditions (Slide #73) <a href=#home>Click Me to scroll to top</a>
```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  filter(adults == 0,children >= 1) %>%
  select(adults, babies, children)
```
</div><div id="q28">
### 28. filter() to select rows based on complicated conditions (Slide #74) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% 
  filter(adults == 1,children >= 1 | babies >=1) %>% 
  select(adults, babies, children)
```
</div><div id="q29">
### 29. count() and arrange() (Slide #76) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% 
  count(market_segment) %>% 
  arrange(desc(n))
```
</div><div id="q30">
### 30. mutate(), select() and arrange() (Slide #77) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% 
  mutate(little_ones = children + babies) %>%
  select(children, babies, little_ones) %>%
  arrange(desc(little_ones))
```
</div><div id="q31">

### 31. mutate(), filter() and select() (Slide #78) <a href=#home>Click Me to scroll to top</a>

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% 
  mutate(little_ones = children + babies) %>%
  filter(little_ones >= 1,hotel == "City Hotel") %>%
  select(hotel, little_ones)
```
</div>